---
title: "Vessel Activity Analysis based on the AIS data"
author: "Min-Ci Sun"
data: December 2023
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vessel Activity Summary based on the AIS data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(VesselSummaryAIS)
```

Since 2012, the U.S. Coast Guard has collected dynamic vessel traffic data, or Automatic Identification System (AIS) data, to ensure the safety of vessel travels. The information includes the vessel's identity, type, position, course, speed, navigational status, and other safety-related information. In 2016, the International Maritime Organization (IMO) implemented the full AIS regulations for commercial vessels, including passenger ships, cargo ships over 300 gross tons, and all types of ships over 500 gross tons. 
However, the AIS data may not be intuitive to use as it collects all vessel navigation information temporally, making it hard to retrieve useful information. Therefore, this project intends to build a package to analyze daily AIS data, providing a tool to better understand vessel activities and vessel compositions.




```{r function}
summarizeship(AISdata, maxLON = -90, minLON = -110, maxLAT = 30, minLAT = 20)
```






