---
title: "Vessel Activity Summary based on AIS data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vessel Activity Summary based on AIS data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## This is the introduction for R package: VesselSummaryAIS 
## Background 

The U.S. Coast Guard has collected dynamic vessel traffic data, or Automatic Identification System (AIS) data, to ensure the safety of vessel travels in North America. Despite its public availability, the AIS data may not be intuitive to use because all the vessels' information is squeezed in a csv file.\ 

**Therefore, this package is designed to analyze daily AIS data, providing a tool for practitioners to better understand the vessel activities and vessel compositions within a specified geographical area.**

<Reference>\
(1)You can download [real AIS data here](https://marinecadastre.gov/ais/) by click *AIS Broadcast Points* and choose a desirable day.\
(2)This [file](https://coast.noaa.gov/data/marinecadastre/ais/data-dictionary.pdf) introduces the funciton of each column.\
(3)Ship types in AIS data are represented by a specific [code](https://coast.noaa.gov/data/marinecadastre/ais/VesselTypeCodes2018.pdf)


```{r setup}
# If you do not have VesselSummaryAIS, use devtools to download.
# install.packages("devtools")
# devtools::install_github("mincisun5296/VesselSummaryAIS")
library(VesselSummaryAIS)
```

## Introduction of AIS data 

The AIS data consists of vessel and operational information for each signal. This package includes a test data (named AISdata) for users to have a basic understanding of its structure.\
You may use the command-- `?AISdata` for more information.\

After obtaining the AIS data from the [website](https://marinecadastre.gov/ais/), unzip the file and utilize the following command to load the data:`AISdata <- read.csv("dataname.csv", header = T)`


```{r}
head(AISdata, 3) # shows first 3 rows
```
*VesselType* is a code to determine the ship type based on Reference [(3)]((https://coast.noaa.gov/data/marinecadastre/ais/VesselTypeCodes2018.pdf)), where the ship type includes
**Cargo, Fishing, Military, Not_available, Others, Passengers, Pleasure, Tanker, and Tugboat**. 

## Function:
### 1.  Vessel Summary within a Specified Geographical Area
The `summarizeship` function allows user to specify the range of latitude and longitude of the study area, summarizing the number and dimensions of each ship type.
```{r}
summarizeship(AISdata, maxLON = -94, minLON = -96, maxLAT = 30, minLAT = 27)

```

### 2.  Vessel Signal Plotting
The `plotvessel` function  generates a visual representation of AIS signal locations. Note that the default ship type is Cargo, but users can input their preferred ship type as well. Other available options include Fishing, Military, Not_available,Others,Passengers,Pleasure,Tanker,and Tugboat within the function parameters.
```{r}
plotvessel(AISdata, studyship = 'Cargo', maxLON = -94, minLON = -96, maxLAT = 30, minLAT = 27)
```

### 3. Speed Distribution
The `speeddist` function creates a histogram illustrating the speed distribution of a specific ship within the study area. Users have the flexibility to input their preferred ship type, with the default set to Cargo.

```{r}
speeddist(AISdata, studyship = 'Fishing', maxLON = -94, minLON = -96, maxLAT = 30, minLAT = 27)
```

### 4. Operating Time Analysis
The `operatingtime` function  analyzes the cumulative operational time of each distinct ship and ship type. Users have the flexibility to set the operational mode by specifying the speed threshold with the parameter `activityspeed`. The 
default speed is 3 knots.\
From the resulting output, the initial data frame showcases the operating time (in minutes) for each vessel, while the subsequent data frame aggregates the total time for each ship type.\

**Please be aware that this function might entail a lengthy computational process as it meticulously calculates the time for each vessel. So be careful about the specified region**

```{r}
# for Vessel
totaltime = operatingtime(AISdata, activityspeed = 3, maxLON = -94, minLON = -96, maxLAT = 30, minLAT = 27 )
head(totaltime[[1]], 5) # show first 5 rows
```

```{r}
# for ship type
totaltime[[2]]
```
